### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - decon - minor edits / writting

The final solutions of this fitting for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon}.

The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film. Note \Tg~ and \Tx$_{1}$ are obtained from the original raw data, not the deconvolution.

@@

>>>>

The final converged solutions of this fitting for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon} respectively. These results are tabulated in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film. Note \Tg~ and \Tx$_{1}$ are obtained from the original raw data, not the deconvolution.

@@

Target error plot?
